\newpage
\section{Risks and Contingency}

Though the premise of this project, an increased-fidelity PDH error-signal
generator, may seem straightforward, there are several nuances which may
complicate development. The models presented in \textbf{Section
\ref{sec:theory}} are meant to give a qualitative overview of why this upgrade
is justified, but they ignore or simplify many parameters.

The signal processing here is mostly considered with the assumption that all
mixing or amplification is linear, and that signal attenuation, if present,
is minimal. In reality, the propagation of the beat-note signals through the
processing electronics may be more complex, with saturation effects and other
nonlinearities coming into effect. The incident side-band beat-note signals,
for example, may be subject to saturation effects in the phototransistor
depending on the incident laser power. This, and other effects, will have to be
carefully accounted for during electrical design. If something is overlooked,
it may be that tuning the locking unit is more difficult than anticipated.

As mentioned, another point of contention is the operation of the EOM unit
itself. Choosing between a readily-available but small-bandwidth low-power EOM
which is tuned around some built-in fixed-bandwidth amplifier, or developing
a custom high-power, wide-bandwidth driver will vastly change the amount of
work that must be done to arrive at a functional unit. Time spent designing an
EOM controller, estimated to take 1-2 weeks, would alternatively be used on
assembly and benchmarking. Making use of a pre-configured EOM would be ideal, but
if the error signal generated by its modulation frequency is less-than-ideal,
analysis and testing of alternative solutions will have to take place.
Implementing the full quantum mechanical description of the Rb87 D2 absorption
spectrum will allow for direct derivation of an optimal modulation frequency.
However this process would likely take the better part of 2-3 weeks, requiring
substantial modelling, simulation and consultation with the sponsor. Having a
ready-made unit perform adequately, but not optimally, is still ideal because
more time can be spent on final debugging, characterization and integration.

The primary detractor to how complete this project will be at delivery
is the amount of custom solutions (CCAs, custom software, etc) that must be
built in-house. Presumably, if the entire control loop can be built from
off-the-shelf components from, for example, Thorlabs and Mini-Circuits,
then a significant amount of time will be devoted to fine-tuning and
benchmarking a ready-to-use assembly. The sponsor has requested two functional,
benchmarked PDH reference units at project completion. It is inconcievable that
these units will not be, at the very least, fully built during this term. Lack
of built PDH reference units, consisting of the opto-electronic assembly and
electronic mixing components, by 2014-12-20 is considered a project failure.
The sponsor has allowed for testing and benchmarking to be completed after
delivery, if absolutely necessary.