\newpage
\section{Deliverables}

\subsection{EOM-based optical breadboard setup}

The sponsor already has optical breadboards, as well as a supply of optical equipment
which we can use.  An optical breadboard must be assembled, in a configuration which
includes the electro-optic modulator (EOM). \\

An EOM must be selected for this purpose which has appropriate characteristics. The
EOM already owned by the Madison group will be appropriated first, with alternate
purchases being made only if necessary. \\

This deliverable should be relatively low-risk, as the sponsor already has a working
setup, and all that is required is to replicate this setup using an EOM instead of an AOM,
and design supporting electronics.

\subsection{Fast Analog Laser Control Feedback Circuit}

An analog feedback circuit must be constructed to provide an error signal.  The feedback circuit should take advantage of the improved frequency response of the EOM (compared to AOM).  It should have a characteristic response time on the order of 1-10MHz, as opposed to the 10kHz response time of the existing AOM-based solution.

\subsection{New vs. Old System Characterization}

The performance of the existing AOM-based system must be measured and compared to the new,
EOM-based system.  Important parameters include:

\begin{itemize}
    \item Laser linewidth
    \item Closeness to expected frequency
    \item Frequency response of the error signal
    \item Noise resistance of the two systems
\end{itemize}

The new system should improve upon the existing system in quality of frequency lock, as well as the speed of the lock.