\newpage
\section*{Glossary}

\begin{tabularx}{\linewidth}{lX}
  {\bf AOM} & Acousto-optic modulator: a device which uses acoustic waves to vary the direction of a light beam, and in turn the distance it must travel, creating a doppler-shifted diffraction pattern. \\
  {\bf CCA} & Circuit Card Assembly: includes a PBC and all of its components,
  sometimes encludes complimentary mechanical components as well. \\
  {\bf EOM} & Electro-optic modulator: also known as a Pockels cell, this
  is an optical medium which is subject to the Pockels effect: electrically
  modulating the phase of an incident electromagnetic wave in the direction
  of propagation.\\
  {\bf EMI} & Electromagnetic Interference: two types: radiated and conducted.\\
  {\bf FO (Receiver)} & Fiber Optic (photosensor unit for detecting fiber optic
  signals).  \\
  {\bf PCB} & Printed Circuit Board. \\
  {\bf PDH} & Pound-Drever-Hall. Refers to a method of generating an RF signal to resolve a frequency selective feature from higher frequency optical signals. \\
  {\bf Pol Cube} & A polarization cube.  Filters light such that horizontally polarized light passes straight through, and vertically polarized light reflects. \\
  {\bf RF} & Radio Frequency. Used to refer to components or systems which
  operate in the 3 kHz - 300 GHz regime. \\
  {\bf VCO} & Voltage Controlled Oscillator, may be crystal or PLL based. \\
  {\bf $V_{PP}$} & Peak-to-peak voltage: the full range of voltage of a
  particular waveform.
\end{tabularx}
